Optimal (Multiway) Spatial Joins

### 2024-06-03 msj.tex
yufei

Next, we will prove 
\myeqn{
    \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')} |\dcross_H(\bm{t})| \cdot |\dcross_V(\bm{t})| \leq \out. \label{eqn:hv:type1:properties:proof-help1}
} 
which implies statement (3) because, for any $\bm{t}$ in the summation, $|\dcross_H(\bm{t})| \ge 1$ and $|\dcross_V(\bm{t})| \ge 1$. Our proof resorts to the algorithm generate-$\J^*$ (see Section~\ref{sec:hv:type1}). This algorithm adds to $\J^*$ exactly as many tuples as calculated by the left hand side of \eqref{eqn:hv:type1:properties:proof-help1}. By statement (1) of Lemma~\ref{lmm:hv:type2:properties}, the $\J^*$ produced must be a subset of $\J(R_1,...,R_{k-2},H,V)$, whose size is $\out$. This establishes the inequality in \eqref{eqn:hv:type1:properties:proof-help1}, which completes the proof of statement (3).

>>>>

Next, we will prove 
\myeqn{
    \sum_{\bm{t}\in \J(R_1',...,R_{k-2}')} |\dcross_H(\bm{t})| \cdot |\dcross_V(\bm{t})| \leq \out. \label{eqn:hv:type1:properties:proof-help1}
} 
which implies statement (3) because, for any $\bm{t}$ in the summation, $|\dcross_H(\bm{t})| \ge 1$ and $|\dcross_V(\bm{t})| \ge 1$. Our proof resorts to the algorithm generate-$\J^*$ (see Section~\ref{sec:hv:type1}). This algorithm adds to $\J^*$ exactly as many tuples as calculated by the left hand side of \eqref{eqn:hv:type1:properties:proof-help1}. By statement (1) of Lemma~\ref{lmm:hv:type2:properties}, the $\J^*$ produced must be a subset of $\J(R_1,...,R_{k-2},H,V)$, whereas $\out = |\J(R_1,...,R_{k-2},H,V)|$. This establishes the inequality in \eqref{eqn:hv:type1:properties:proof-help1}, which completes the proof of statement (3).
